---
title: "Lab 07 - Conveying the right message through visualisation"
author: "Ryan Wheat"
date: "03/7/2023"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercise 1

The thing that is so (purposefully) misleading about this graph is that the two groups are not being graphed on the same y-axis. 

Thus, at face-value, this visual seems to display how mask mandates are more effective at reducing the number of COVID cases in counties that adopt them than counties which do not, and that this leads to fewer COVID cases overall.

Instead, this visual should show that mask mandates reduce COVID cases in counties that adopt them -- but that counties which don't have mask mandates still have fewer people test positive for COVID overall.

```{r create-dataframe}

df <- tribble(
  ~date, ~count, ~mandate,
  "7/12/2020", 26, "Yes",
  "7/12/2020", 9.9, "No",
  "7/13/2020", 20,"Yes",
  "7/13/2020", 9, "No",
  "7/14/2020", 20, "Yes",
  "7/14/2020", 9.3, "No",
  "7/15/2020", 20.5, "Yes",
  "7/15/2020", 9.9, "No",
  "7/16/2020", 20, "Yes",
  "7/16/2020", 10, "No",
  "7/17/2020", 20, "Yes",
  "7/17/2020", 9.3, "No",
  "7/18/2020", 20.5, "Yes",
  "7/18/2020", 9.3, "No",
  "7/19/2020", 20, "Yes",
  "7/19/2020", 9, "No",
  "7/20/2020", 20.8, "Yes",
  "7/20/2020", 8.4, "No",
  "7/21/2020", 21.5, "Yes",
  "7/21/2020", 8.5, "No",
  "7/22/2020", 20, "Yes",
  "7/22/2020", 8.8, "No",
  "7/23/2020", 20, "Yes",
  "7/23/2020", 8.5, "No",
  "7/24/2020", 20.6, "Yes",
  "7/24/2020", 9.9, "No",
  "7/25/2020", 19, "Yes",
  "7/25/2020", 10, "No",
  "7/26/2020", 19.5, "Yes",
  "7/26/2020", 10.1, "No",
  "7/27/2020", 17, "Yes",
  "7/27/2020", 9.5, "No",
  "7/28/2020", 16.4, "Yes",
  "7/28/2020", 9.6, "No",
  "7/29/2020", 16.6, "Yes",
  "7/29/2020", 9.7, "No",
  "7/30/2020", 16.8, "Yes",
  "7/30/2020", 10, "No",
  "7/31/2020", 16, "Yes",
  "7/31/2020", 8.8, "No",
  "8/1/2020", 16.2, "Yes",
  "8/1/2020", 9, "No",
  "8/2/2020", 15.9, "Yes",
  "8/2/2020", 8.8, "No",
  "8/3/2020", 16, "Yes",
  "8/3/2020", 9.1, "No",
)

```


### Exercise 2

```{r create-visual}

df %>%
  ggplot(aes(x = date, y = count, group = mandate, color = mandate)) + geom_line(linewidth = 1) + theme_dark() + labs(title = "COVID-19 Trends In Kansas 2020", x = "Date", y = "COVID Cases per 100K People", color = "Mask Mandate County")
  

```

### Exercise 3

In the above plot, it is abundantly clear that, even though transmission rates do decrease over time, mask mandate counties did NOT end up with fewer COVID cases per 100,000 people than non-mask mandate counties. In fact, non-mask mandate counties had consistently lower COVID transmisison rates than did mask mandate counties.

### Exercise 4

This visualization suggests that counties which adopted mask mandates are the ones that very much needed to do so, because they had high initial rates of COVID transmission that needed to be reduced.

Yet, they still have higher transmission rates than counties which did not adopt a mask mandate. Rather than indicating that these counties need to do-away with mask mandates, this suggests to me that there is a selection effect going on here.

That is, non-mask mandate counties never NEEDED to adopt a mandate, because their infection rates were always relatively low. Conversely, counties with a mask mandate needed to enforce masking because they had relatively high transmission rates to begin with. Thus, even though they don't reach non-masking levels, it would be difficult to do so from their initial position over the course of one month.

Therefore, I'm hesitant to draw any hard conclusions from these data.


...

Add exercise headings as needed.
